### 2016-09-02 lineups.Rnw
remove results that were printing that shouldn't have been

<<get_res, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.cap="Boxplot showing the percent of users correctly choosing the alternative model in all 25 lineups. In 15 out of 25 lineups, no user picked the correct plot. The maximum was 64.00\\%, and the second highest was 35.29\\% correct.", fig.height=3>>=
ids <- readr::read_csv("https://raw.githubusercontent.com/erichare/lineups/f19635a00507210013ba9e631761ad0c89a6564d/experiments/turk21/details/picture-details.csv")
tab <- read.csv("Results/turk21_users.csv")
tab2 <- unique(tab)
#length(unique(tab2$nick_name))
#head(sort(table(tab2$nick_name),decreasing = T))
#tab2 %>% filter(nick_name == "A3U3L1XQVR362A")
#tab2 %>% filter(nick_name == "ADTIO3A6TM9CG")
#tab2 %>% filter(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10])
res <- read.csv("Results/turk21_feedback.csv", stringsAsFactors = F)
# remove people who only completed 1 plot
res <- res %>% filter(!(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10]))
# need to repeat rows with weights for people who selected multiple plots.
res_norpt <- res[-grep(",", res$response_no),]  
res_rpt <- res[grep(",", res$response_no),]  
res_rpt$response_no
library(stringr)
# count # of responses (ttr = times to repeat)
ttr <- str_count(string = res_rpt$response_no, pattern = ",") + 1
rpt_rows <- rep(1:nrow(res_rpt), ttr)
rpt_rows2 <- res_rpt[rpt_rows,]
rpt_rows2$count_response <- unlist(sapply(ttr, seq_len))
rpt_rows2$weight <- 1/rep(ttr, ttr)
split_rows <- strsplit(rpt_rows2$response_no, ",")
rpt_rows2$response_no2 <- NA
for(i in 1:nrow(rpt_rows2)){
  rpt_rows2$response_no2[i] <- split_rows[[i]][rpt_rows2$count_response[i]]
}

res_norpt$count_response <- 1 
res_norpt$response_no2 <- res_norpt$response_no
res_norpt$tot_response <- 1 
res_norpt$weight <- 1
# res with weight column   
new_res <- rbind(res_norpt, rpt_rows2)

#intersect(names(ids), names(res))
res2 <- left_join(new_res, ids, by = 'pic_id')
res2$correct <- res2$response_no == res2$obs_plot_location
res2$time <- res2$end_time - res2$start_time
res2$lineup_name <- as.factor(paste(res2$test_param, res2$param_value))
# with the correct labels (in order of data plot w/value most different from rest to least different)
more_details <- read.csv("experimentdetails_Aug31.csv", stringsAsFactors = F)
res3 <- left_join(res2, more_details, by = c("data_name" = "lineup_filename"))
# higest jtts are: reps 18, 20, 6, 19, 3 with 
              # jtts of 40, 24, 18,17, 9
head(res3)
res3$group_name <- paste0(res3$group, " #", res3$group.rep)

@@

\begin{figure}
\begin{subfigure}[c]{.45\textwidth}
\textbf{Gender:} \\
<<tab_demo, echo=FALSE, results='asis'>>=
t1 <- t(data.frame(table(tab2$gender)))
rownames(t1) <- c("Gender:", "Count:")
colnames(t1) <- t1[1,]
t1 <- t1[2,]
t1[as.numeric(t1) < 5] <- "*"
kable(t1, format = 'latex')
@
\vspace{.5cm}
\textbf{Education Level:} \\
<<tab_demo3, echo=FALSE, results='asis'>>=
t3 <- t(data.frame(table(tab2$academic_study)))
rownames(t3) <- c("Highest Education:", "Count:")
colnames(t3) <- t3[1,]
t3 <- t3[2,]
t3[as.numeric(t3) < 5] <- "*"
kable(t3, format = 'latex')
@
\end{subfigure}\hfill
\begin{subfigure}[c]{.45\textwidth}
\centering
\textbf{Age Group:} \\
<<tab_demo2, echo=FALSE, results='asis'>>=
t2 <- t(data.frame(table(tab2$age)))
rownames(t2) <- c("Age:", "Count:")
colnames(t2) <- t2[1,]
t2 <- t2[2,]
names(t2)
t2.2 <- t2
t2.2 <- t2.2[1:7]
names(t2.2)[6:7] <- c("46-55", "Over 55")
t2.2[6:7] <- c(sum(as.numeric(t2[6:7])), sum(as.numeric(t2[8:9])))
kable(t2, format = 'latex')
@
\end{subfigure}
\caption{\label{fig:demos} Demographic information on the Amazon Turk users participating in the experiment. Asterisks (*) indicate less than 5 responses.}
\end{figure}

>>>>

<<get_res, echo=FALSE, warning=FALSE, message=FALSE, fig.align="center", fig.cap="Boxplot showing the percent of users correctly choosing the alternative model in all 25 lineups. In 15 out of 25 lineups, no user picked the correct plot. The maximum was 64.00\\%, and the second highest was 35.29\\% correct.", fig.height=3>>=
ids <- readr::read_csv("https://raw.githubusercontent.com/erichare/lineups/f19635a00507210013ba9e631761ad0c89a6564d/experiments/turk21/details/picture-details.csv")
tab <- read.csv("Results/turk21_users.csv")
tab2 <- unique(tab)
#length(unique(tab2$nick_name))
#head(sort(table(tab2$nick_name),decreasing = T))
#tab2 %>% filter(nick_name == "A3U3L1XQVR362A")
#tab2 %>% filter(nick_name == "ADTIO3A6TM9CG")
#tab2 %>% filter(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10])
res <- read.csv("Results/turk21_feedback.csv", stringsAsFactors = F)
# remove people who only completed 1 plot
res <- res %>% filter(!(nick_name %in% names(table(res$nick_name))[table(res$nick_name) != 10]))
# need to repeat rows with weights for people who selected multiple plots.
res_norpt <- res[-grep(",", res$response_no),]  
res_rpt <- res[grep(",", res$response_no),]

library(stringr)
# count # of responses (ttr = times to repeat)
ttr <- str_count(string = res_rpt$response_no, pattern = ",") + 1
rpt_rows <- rep(1:nrow(res_rpt), ttr)
rpt_rows2 <- res_rpt[rpt_rows,]
rpt_rows2$count_response <- unlist(sapply(ttr, seq_len))
rpt_rows2$weight <- 1/rep(ttr, ttr)
split_rows <- strsplit(rpt_rows2$response_no, ",")
rpt_rows2$tot_response <- rep(ttr, ttr)
rpt_rows2$response_no2 <- NA
for(i in 1:nrow(rpt_rows2)){
  rpt_rows2$response_no2[i] <- split_rows[[i]][rpt_rows2$count_response[i]]
}

res_norpt$count_response <- 1 
res_norpt$weight <- 1
res_norpt$response_no2 <- res_norpt$response_no
res_norpt$tot_response <- 1

# res with weight column   
new_res <- rbind(res_norpt, rpt_rows2)

#intersect(names(ids), names(res))
res2 <- left_join(new_res, ids, by = 'pic_id')
res2$correct <- res2$response_no == res2$obs_plot_location
res2$time <- res2$end_time - res2$start_time
res2$lineup_name <- as.factor(paste(res2$test_param, res2$param_value))
# with the correct labels (in order of data plot w/value most different from rest to least different)
more_details <- read.csv("experimentdetails_Aug31.csv", stringsAsFactors = F)
res3 <- left_join(res2, more_details, by = c("data_name" = "lineup_filename"))
# higest jtts are: reps 18, 20, 6, 19, 3 with 
              # jtts of 40, 24, 18,17, 9
res3$group_name <- paste0(res3$group, " #", res3$group.rep)

@@

\begin{figure}
\begin{subfigure}[c]{.45\textwidth}
\textbf{Gender:} \\
<<tab_demo, echo=FALSE, results='asis'>>=
t1 <- t(data.frame(table(tab2$gender)))
rownames(t1) <- c("Gender:", "Count:")
colnames(t1) <- t1[1,]
t1 <- t1[2,]
t1[as.numeric(t1) < 5] <- "*"
kable(t1, format = 'latex')
@
\vspace{.5cm}
\textbf{Education Level:} \\
<<tab_demo3, echo=FALSE, results='asis'>>=
t3 <- t(data.frame(table(tab2$academic_study)))
rownames(t3) <- c("Highest Education:", "Count:")
colnames(t3) <- t3[1,]
t3 <- t3[2,]
t3[as.numeric(t3) < 5] <- "*"
kable(t3, format = 'latex')
@
\end{subfigure}\hfill
\begin{subfigure}[c]{.45\textwidth}
\centering
\textbf{Age Group:} \\
<<tab_demo2, echo=FALSE, results='asis'>>=
t2 <- t(data.frame(table(tab2$age)))
rownames(t2) <- c("Age:", "Count:")
colnames(t2) <- t2[1,]
t2 <- t2[2,]
t2.2 <- t2
t2.2 <- t2.2[1:7]
names(t2.2)[6:7] <- c("46-55", "Over 55")
t2.2[6:7] <- c(sum(as.numeric(t2[6:7])), sum(as.numeric(t2[8:9])))
kable(t2.2, format = 'latex')
@
\end{subfigure}
\caption{\label{fig:demos} Demographic information on the Amazon Turk users participating in the experiment. Asterisks (*) indicate less than 5 responses.}
\end{figure}
